They're on Fire: Team Momentum in Round-Based First Person Shooter Esports

### 2022-07-25 presentation.qmd
more val cleaning, re-arrange plots

---
title: '"Turned on!": Momentum in Round-Based First Person Shooter Esports'
author: 'Tony ElHabr'
format:
  revealjs:
    slide-number: true
    incremental: false
    theme: [dark, theme.scss]
execute: 
  include: false
  echo: false
  eval: false
---

@@

.dpi <- 300
save_plot_for_slide <- function(
    p, 
    filename = paste0(str_remove(deparse(substitute(p)), '^p_'), '.png'), 
    width = 7.5, 
    height = width / 1.5,
    units = 'px',
    dpi = .dpi,
    # game = c('cod', 'val'),
    ...
) {

  path <- ggsave(
    plot = p,
    filename = filename,
    width = width * dpi,
    height = height * dpi,
    units = units,
    dpi = dpi,
    ...
  )
  is_cod <- filename |> str_detect('cod_')
  game <- ifelse(is_cod, 'cod', 'val')
  logo_scale <- ifelse(is_cod, 0.15, 0.07)
  add_logo(
    path,
    path_logo = file.path('images', sprintf('%s.png', game)),
    delete = FALSE,
    path_suffix = '',
    logo_scale = logo_scale,
    idx_x = 0.99,
    idx_y = 0.01,
    adjust_x = FALSE
  )
}

@@

![](cod_o_round_win_prop.png){fig-align="center"}

@@

![](cod_o_round_win_prop_over_expected.png){fig-align="center"}

@@

![](val_o_round_win_prop.png){fig-align="center"}

@@

![](cod_o_series_win_prop.png){fig-align="center"}

@@

![](cod_o_series_win_prop_over_expected.png){fig-align="center"}

@@

![](val_o_series_win_prop.png){fig-align="center"}

@@

![](val_o_series_win_prop_over_expected.png){fig-align="center"}

@@

## Are offensive win %'s different in round 1 ([COD SnD]{.cod}?

@@

cod_res_r1 <- cod_rounds |> 
  mutate(
    map = sprintf('%s - %s (%s)', map, game, year)
  ) |> 
  plot_round_vs_post_round_slope_chart(1, game = 'cod')

@@

![](cod_o_win_r1_vs_post_round_prop.png){fig-align="center"}

## Are offensive win %'s different in round 1 ([Valorant]{.valorant}?

@@

![](val_o_win_r1_vs_post_round_prop.png){fig-align="center"}

## What are the most common series winning states?

@@

summarize_streaks <- function(rounds, game = c('cod', 'val')) {
  rounds <- val_rounds
  game = 'val'
  .max_round <- ifelse(game == 'cod', 11, 25)

  sudden_death_rounds <- rounds |> 
    filter(max_round > .max_round)

  rounds1 <- rounds
  ## should only happen in val
  if(nrow(sudden_death_rounds) > 0) {

    sudden_death_series_ids <- sudden_death_rounds |> 
      distinct(series_id)

    imputed_suddent_death_rounds <- sudden_death_rounds |> 
      mutate(
        round = .max_round
      ) |> 
      select(series_id, round, is_offense) |> 
      inner_join(
        rounds,
        by = c('series_id', 'round', 'is_offense')
      )

    rounds <- bind_rows(
      rounds |> 
        filter(max_round <= .max_round),
      imputed_suddent_death_rounds
    )
  }

@@

  actual_round_streaks <- rounds |> 
    filter(round <= .max_round) |> 
    filter(win_series) |> 
    mutate(across(win_round, as.integer)) |> 
    group_by(series_id) |> 
    summarize(
      wins = max(cumu_w),
      losses = max(cumu_l),
      ws = paste0(win_round, collapse = '')
    ) |> 
    ungroup() |> 
    mutate(n_rounds = wins + losses) |> 
    unite(
      record, wins, losses, sep = '-'
    ) |>
    count(record, n_rounds, ws, sort = TRUE) |> 
    mutate(prop = n / sum(n))

@@

  list(
    rounds = series_streak_prop,
    series = series_outcome_prop
  )
}

cod_streaks_res <- cod_rounds |> summarize_streaks(game = 'cod')
val_streaks_res <- val_rounds |> summarize_streaks(game = 'val')
cod_long_series_outcome_prop <- cod_streaks_res$series |>
  select(
    record,
    n = n_actual,
    `3` = prop_actual,
    `2` = prop_expected,
    `1` = prop_diff
  ) |> 
  pivot_longer(
    matches('[123]'),
    names_to = 'outcome_idx',
    values_to = 'value'
  ) |> 
  mutate(across(outcome_idx, as.integer))

cod_max_diff_series_outcome_prop <- cod_long_series_outcome_prop |> 
  filter(outcome_idx == 1) |> 
  pull(value) |> 
  abs() |> 
  max()

p_cod_series_outcome_prop_over_expected <- cod_long_series_outcome_prop |> 
  ggplot() +
  aes(x = record, y = outcome_idx) +
  geom_tile(
    data = cod_long_series_outcome_prop |> filter(outcome_idx > 1),
    show.legend = FALSE,
    # height = 0.8,
    aes(fill = value)
  ) +
  ggsci::scale_fill_material(
    palette = 'light-blue'
  ) +
  ggnewscale::new_scale_fill() +
  geom_tile(
    data = cod_long_series_outcome_prop |> filter(outcome_idx == 1),
    show.legend = FALSE,
    height = 0.8,
    aes(fill = value)
  ) +
  scale_fill_gradient2(
    low = extract_ggsci_mid_color('purple'),
    high = extract_ggsci_mid_color('green'),
    mid = 'white',
    midpoint = 0,
    limits = c(
      -cod_max_diff_series_outcome_prop, 
      +cod_max_diff_series_outcome_prop
    )
  ) +
  geom_text(
    data = cod_long_series_outcome_prop |> filter(outcome_idx == 3),
    color = blackish_background,
    size = 11 / .pt,
    aes(label = sprintf('%.1f%%\n(%s)', 100 * value, scales::comma(n)))
  ) +
  geom_text(
    data = cod_long_series_outcome_prop |> filter(outcome_idx == 2),
    color = blackish_background,
    size = 11 / .pt,
    aes(label = sprintf('%.1f%%', 100 * value))
  ) +
  geom_text(
    data = cod_long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) != max(abs(value))),
    color = blackish_background,
    size = 11 / .pt,
    aes(label = sprintf('%+.1f%%', 100 * value))
  ) +
  geom_text(
    data = cod_long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) == max(abs(value))),
    color = 'white',
    size = 11 / .pt,
    aes(label = sprintf('%+.1f%%', 100 * value))
  ) +
  scale_x_discrete(
    position = 'top',
    expand = c(0, 0)
  ) +
  scale_y_continuous(
    labels = c('Diff.', 'Expected', 'Actual'),
    breaks = 1:3,
    expand = c(0, 0)
  ) +
  theme(
    panel.grid.major = element_blank(),
    axis.title = element_text(hjust = 0.5),
    plot.title = ggtext::element_markdown(hjust = 0.5),
    axis.text = element_text(size = 16, face = 'bold')
  ) +
  labs(
    title = 'Series outcome %',
    x = NULL,
    y = NULL
  ) +
  common_cod_labs() 
p_cod_series_outcome_prop_over_expected
save_plot_for_slide(p_cod_series_outcome_prop_over_expected)
```

![](cod_series_outcome_prop_over_expected.png){fig-align="center"}

## When do back-to-back round wins occur?

@@

p_cod_b2b_round_win_prop <- cod_b2b_round_win_prop |> 
  ggplot() +
  b2b_round_win_prop_tile_layer(
    .df = cod_b2b_round_win_prop, 
    .round = 7, 
    .palette = 'pink', 
    .is_new = FALSE
  ) +
  b2b_round_win_prop_tile_layer(
    .df = cod_b2b_round_win_prop, 
    .round = 8, 
    .palette = 'light-blue'
  ) +
  b2b_round_win_prop_tile_layer(
    .df = cod_b2b_round_win_prop, 
    .round = 9, 
    .palette = 'light-green'
  ) +
  b2b_round_win_prop_tile_layer(
    .df = cod_b2b_round_win_prop, 
    .round = 10, 
    .palette = 'amber'
  ) +
  b2b_round_win_prop_tile_layer(
    .df = cod_b2b_round_win_prop, 
    .round = 11, 
    .palette = 'deep-orange
  ') +
  b2b_round_win_prop_text_layers(.df = cod_b2b_round_win_prop) +
  scale_x_continuous(
    labels = 2:11,
    breaks = seq(2.5, 11.5, by = 1),
    expand = c(0, 0.5)
  ) +
  scale_y_continuous(
    labels = 7:11,
    breaks = seq(7.5, 11.5, by = 1),
    expand = c(0, 0)
  ) +
  theme(
    panel.grid.major = element_blank(),
    axis.title = element_text(hjust = 0.5),
    plot.title = ggtext::element_markdown(hjust = 0.5),
    axis.text = element_text(size = 16, face = 'bold')
  ) +
  common_cod_labs() +
  labs(
    title = 'Back-to-back round win %',
    x = 'Round',
    y = '# of cod_rounds in Complete Series'
  ) + 
  geom_text(
    data = tibble(
      label = 'Back-to-back wins occur most\nfrequently in the last round.',
      x = 9.5,
      y = 8.5
    ),
    size = 9 / .pt,
    fontface = 'bold',
    color = 'white',
    hjust = 0,
    vjust = 0.5,
    aes(x = x, y = y, label = label)
  ) +
  map(
    cod_b2b_round_win_prop_arws |> group_split(rn), 
    function(.x) {
      geom_curve(
        data = data.frame(),
        color = 'white',
        arrow = arw,
        aes(x = .x$x, y = .x$y, xend = .x$xend, yend = .x$yend),
        curvature = .x$curvature
      )
    }
  )
p_cod_b2b_round_win_prop
save_plot_for_slide(p_cod_b2b_round_win_prop)
# ## now accounting for number of cod_rounds that end up being played AND series winners...
# cod_rounds |> 
#   filter(win_series, n_rounds > 6L) |> 
#   summarize_b2b_round_wins(n_rounds)
# 
# ## and the losers...
# cod_rounds |> 
#   filter(!win_series) |> 
#   summarize_b2b_round_wins(n_rounds)
```

![](cod_b2b_round_win_prop.png){fig-align="center"}

@@

>>>>

---
title: "They're on Fire: Team Momentum in Round-Based First Person Shooter Esports"
author: 'Tony ElHabr'
format:
  revealjs:
    slide-number: true
    incremental: false
    theme: [dark, theme.scss]
execute: 
  include: false
  echo: false
  eval: false
---

@@

.dpi <- 300
save_plot_for_slide <- function(
    p, 
    filename = paste0(str_remove(deparse(substitute(p)), '^p_'), '.png'), 
    width = 7.5, 
    height = width / 1.5,
    units = 'px',
    dpi = .dpi,
    ...
) {

  path <- ggsave(
    plot = p,
    filename = file.path('plots', filename),
    width = width * dpi,
    height = height * dpi,
    units = units,
    dpi = dpi,
    ...
  )
  is_cod <- filename |> str_detect('cod_')
  game <- ifelse(is_cod, 'cod', 'val')
  logo_scale <- ifelse(is_cod, 0.15, 0.07)
  add_logo(
    path,
    path_logo = file.path('images', sprintf('%s.png', game)),
    delete = FALSE,
    path_suffix = '',
    logo_scale = logo_scale,
    idx_x = 0.99,
    idx_y = 0.01,
    adjust_x = FALSE
  )
}

@@

![](plots/cod_o_round_win_prop.png){fig-align="center"}

@@

![](plots/cod_o_round_win_prop_over_expected.png){fig-align="center"}

@@

![](plots/val_o_round_win_prop.png){fig-align="center"}

@@

![](plots/cod_o_series_win_prop.png){fig-align="center"}

@@

![](plots/cod_o_series_win_prop_over_expected.png){fig-align="center"}

@@

![](plots/val_o_series_win_prop.png){fig-align="center"}

@@

![](plots/val_o_series_win_prop_over_expected.png){fig-align="center"}

@@

## Are offensive win %'s different in round 1 ([COD SnD]{.cod})?

@@

cod_res_r1 <- cod_rounds |> 
  plot_round_vs_post_round_slope_chart(1, game = 'cod')

@@

![](plots/cod_o_win_r1_vs_post_round_prop.png){fig-align="center"}

## Are offensive win %'s different in round 1 ([Valorant]{.valorant})?

@@

![](plots/val_o_win_r1_vs_post_round_prop.png){fig-align="center"}

## What are the most common series winning states ([COD SnD]{.cod})?

@@

summarize_streaks <- function(rounds, game = c('cod', 'val')) {
  if (game == 'cod') {
    .max_round <- 11
    .adj <- 0
  } else {
    .max_round <- 25
    .adj <- 1
  }

@@

  actual_round_streaks <- rounds |> 
    filter(round <= (.max_round - .adj)) |> 
    filter(win_series) |> 
    mutate(across(win_round, as.integer)) |> 
    group_by(series_id) |> 
    summarize(
      wins = max(cumu_w),
      losses = max(cumu_l),
      ws = paste0(win_round, collapse = '')
    ) |> 
    ungroup() |> 
    mutate(n_rounds = wins + losses) |> 
    unite(
      record, wins, losses, sep = '-'
    ) |>
    count(record, n_rounds, ws, sort = TRUE) |> 
    mutate(prop = n / sum(n))

@@

  list(
    rounds = round_streak_prop,
    series = series_outcome_prop
  )
}

plot_series_outcome_prop_over_expected <- function(series_outcome_prop, game) {
  if (game == 'cod') {
    .lvls <- sprintf('6-%d', 0:5)
    .axis_x_text_size <- 14
  } else {
    .lvls <- c(sprintf('13-%d', 0:11), '12-12')
    .axis_x_text_size <- 12
  }

  long_series_outcome_prop <- series_outcome_prop |>
    select(
      record,
      n = n_actual,
      `3` = prop_actual,
      `2` = prop_expected,
      `1` = prop_diff
    ) |> 
    pivot_longer(
      matches('[123]'),
      names_to = 'outcome_idx',
      values_to = 'value'
    ) |> 
    mutate(
      across(outcome_idx, as.integer),
      across(record, ~factor(.x, levels = .lvls))
    )

  max_diff_series_outcome_prop <- long_series_outcome_prop |> 
    filter(outcome_idx == 1) |> 
    pull(value) |> 
    abs() |> 
    max()

  long_series_outcome_prop |> 
    ggplot() +
    aes(x = record, y = outcome_idx) +
    geom_tile(
      data = long_series_outcome_prop |> filter(outcome_idx > 1),
      show.legend = FALSE,
      # height = 0.8,
      aes(fill = value)
    ) +
    ggsci::scale_fill_material(
      palette = 'light-blue'
    ) +
    ggnewscale::new_scale_fill() +
    geom_tile(
      data = long_series_outcome_prop |> filter(outcome_idx == 1),
      show.legend = FALSE,
      height = 0.8,
      aes(fill = value)
    ) +
    scale_fill_gradient2(
      low = extract_ggsci_mid_color('purple'),
      high = extract_ggsci_mid_color('green'),
      mid = 'white',
      midpoint = 0,
      limits = c(
        -max_diff_series_outcome_prop, 
        +max_diff_series_outcome_prop
      )
    ) +
    geom_text(
      data = long_series_outcome_prop |> filter(outcome_idx == 3),
      color = blackish_background,
      size = 11 / .pt,
      aes(label = sprintf('%.1f%%\n(%s)', 100 * value, scales::comma(n)))
    ) +
    geom_text(
      data = long_series_outcome_prop |> filter(outcome_idx == 2),
      color = blackish_background,
      size = 11 / .pt,
      aes(label = sprintf('%.1f%%', 100 * value))
    ) +
    geom_text(
      data = long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) != max(abs(value))),
      color = blackish_background,
      size = 11 / .pt,
      aes(label = sprintf('%+.1f%%', 100 * value))
    ) +
    geom_text(
      data = long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) == max(abs(value))),
      color = 'white',
      size = 11 / .pt,
      aes(label = sprintf('%+.1f%%', 100 * value))
    ) +
    scale_x_discrete(
      position = 'top',
      expand = c(0, 0)
    ) +
    scale_y_continuous(
      labels = c('Diff.', 'Expected', 'Actual'),
      breaks = 1:3,
      expand = c(0, 0)
    ) +
    theme(
      panel.grid.major = element_blank(),
      axis.title = element_text(hjust = 0.5),
      plot.title = ggtext::element_markdown(hjust = 0.5),
      axis.text = element_text(size = 14, face = 'bold'),
      axis.text.x = element_text(size = .axis_x_text_size, face = 'bold')
    ) +
    labs(
      title = 'Series outcome %',
      x = NULL,
      y = NULL
    )
}

cod_streaks_res <- cod_rounds |> summarize_streaks('cod')

p_cod_series_outcome_prop_over_expected <- cod_streaks_res$series |> 
  plot_series_outcome_prop_over_expected('cod') +
  common_cod_labs()
p_cod_series_outcome_prop_over_expected
save_plot_for_slide(p_cod_series_outcome_prop_over_expected)
```

![](plots/cod_series_outcome_prop_over_expected.png){fig-align="center"}

## What are the most common series winning states ([Valorant]{.valorant})?

```{r}
#| label: p_val_series_outcome_prop_over_expected
val_streaks_res <- val_rounds |> summarize_streaks('val')

p_val_series_outcome_prop_over_expected <- val_streaks_res$series |> 
  plot_series_outcome_prop_over_expected('val') +
  common_val_labs()
p_val_series_outcome_prop_over_expected
save_plot_for_slide(p_val_series_outcome_prop_over_expected)
```

![](plots/val_series_outcome_prop_over_expected.png)

```{r}
#| label: altnerative-to-p=0.5-method-1
## p. 365 on https://math.mit.edu/classes/18.095/2016IAP/lec9/Sports_Mosteller1952_WorldSeries.pdf
theoretical_cod_series_length <- function(p) {
  6 * prob_of_series_lasting_n_games(n = 6, p = p, max_round = 11) +
    7 * prob_of_series_lasting_n_games(n = 7, p = p, max_round = 11) + 
    8 * prob_of_series_lasting_n_games(n = 8, p = p, max_round = 11) + 
    9 * prob_of_series_lasting_n_games(n = 9, p = p, max_round = 11) +
    10 * prob_of_series_lasting_n_games(n = 10, p = p, max_round = 11) +
    11 * prob_of_series_lasting_n_games(n = 11, p = p, max_round = 11)
}

cod_ps <- tibble(p = seq(0.5, 0.7, by = 0.0025))

cod_theoretical_series_lengths <- cod_ps |> 
  mutate(
    theoretical_series_length = map_dbl(p, theoretical_cod_series_length)
  )

cod_rounds_per_series <- cod_streaks_res$series |> 
  summarize(
    actual = sum(n_rounds * prop_actual),
    expected = sum(n_rounds * prop_expected)
  )

cod_theoretical_constant_p <- cod_theoretical_series_lengths |> 
  mutate(
    diff = theoretical_series_length - cod_rounds_per_series$actual
  ) |> 
  slice_min(abs(diff), n = 1) |> 
  pull(p)
cod_theoretical_constant_p
```

```{r}
#| label: altnerative-to-p=0.5-method-2
pluck_cod_n <- function(.n_rounds) {
  cod_streaks_res$series |>
    filter(n_rounds == .n_rounds) |> 
    pull(n_actual)
}

n6 <- pluck_cod_n(6)
n7 <- pluck_cod_n(7)
n8 <- pluck_cod_n(8)
n9 <- pluck_cod_n(9)
n10 <- pluck_cod_n(10)
n11 <- pluck_cod_n(11)
pm <- pmin(n6, n7, n8, n9, n10, n11)
n6adj <- round(10 * n6 / pm)
n7adj <- round(10 * n7 / pm)
n8adj <- round(10 * n8 / pm)
n9adj <- round(10 * n9 / pm)
n10adj <- round(10 * n10 / pm)
n11adj <- round(10 * n11 / pm)

maximize_cod_series_p <- function(p) {
  prob_of_series_lasting_n_games(n = 6, p = p, max_round = 11)^n6adj *
    prob_of_series_lasting_n_games(n = 7, p = p, max_round = 11)^n7adj * 
    prob_of_series_lasting_n_games(n = 8, p = p, max_round = 11)^n8adj * 
    prob_of_series_lasting_n_games(n = 9, p = p, max_round = 11)^n9adj *
    prob_of_series_lasting_n_games(n = 10, p = p, max_round = 11)^n10adj * 
    prob_of_series_lasting_n_games(n = 11, p = p, max_round = 11)^n11adj
}

cod_theoretical_constant_p <- cod_ps |> 
  mutate(
    theoretical_series_length = map_dbl(p, maximize_cod_series_p)
  )

cod_theoretical_constant_p <- cod_theoretical_constant_p |> 
  slice_max(theoretical_series_length, n = 1) |> 
  pull(p)
cod_theoretical_constant_p

m <- matrix(c(cod_streaks_res$series$n_actual, cod_streaks_res$series$n_expected), ncol = 2)
dimnames(m) <- list(n_rounds = as.character(6:11), kind = c('actual', 'expected'))
ch <- chisq.test(m)
# ch$expected
# chance_numbers <- tibble(
#   league = rep(c('mlb', 'nba', 'nhl'), each = 4),
#   i = rep(4:7, 3),
#   a = c(
#     c(0.1894, 0.215, 0.215, 0.3895),
#     c(0.1324, 0.25, 0.3382, 0.2794),
#     c(0.2532, 0.2405, 0.3038, 0.2025)
#   ),
#   e = rep(c(0.125, 0.25, 0.3125, 0.3125), 3)
# )
# chance_numbers |> filter(league == 'mlb') |> select(a, e) |> chisq.test()
```

## When do back-to-back round wins occur ([COD SnD]{.cod})?

@@

p_cod_b2b_round_win_prop <- cod_b2b_round_win_prop |> 
  ggplot() +
  b2b_round_win_prop_tile_layer(
    .df = cod_b2b_round_win_prop, 
    .round = 7, 
    .palette = 'pink', 
    .is_new = FALSE
  ) +
  b2b_round_win_prop_tile_layer(
    .df = cod_b2b_round_win_prop, 
    .round = 8, 
    .palette = 'light-blue'
  ) +
  b2b_round_win_prop_tile_layer(
    .df = cod_b2b_round_win_prop, 
    .round = 9, 
    .palette = 'light-green'
  ) +
  b2b_round_win_prop_tile_layer(
    .df = cod_b2b_round_win_prop, 
    .round = 10, 
    .palette = 'amber'
  ) +
  b2b_round_win_prop_tile_layer(
    .df = cod_b2b_round_win_prop, 
    .round = 11, 
    .palette = 'deep-orange'
  ) +
  b2b_round_win_prop_text_layers(.df = cod_b2b_round_win_prop) +
  scale_x_continuous(
    labels = 2:11,
    breaks = seq(2.5, 11.5, by = 1),
    expand = c(0, 0.5)
  ) +
  scale_y_continuous(
    labels = 7:11,
    breaks = seq(7.5, 11.5, by = 1),
    expand = c(0, 0)
  ) +
  theme(
    panel.grid.major = element_blank(),
    axis.title = element_text(hjust = 0.5),
    plot.title = ggtext::element_markdown(hjust = 0.5),
    axis.text = element_text(size = 16, face = 'bold')
  ) +
  common_cod_labs() +
  labs(
    title = 'Back-to-back round win %',
    x = 'Round',
    y = '# of cod_rounds in Complete Series'
  ) + 
  geom_text(
    data = tibble(
      label = 'Back-to-back wins occur most\nfrequently in the last round.',
      x = 9.5,
      y = 8.5
    ),
    size = 9 / .pt,
    fontface = 'bold',
    color = 'white',
    hjust = 0,
    vjust = 0.5,
    aes(x = x, y = y, label = label)
  ) +
  map(
    cod_b2b_round_win_prop_arws |> group_split(rn), 
    function(.x) {
      geom_curve(
        data = data.frame(),
        color = 'white',
        arrow = arw,
        aes(x = .x$x, y = .x$y, xend = .x$xend, yend = .x$yend),
        curvature = .x$curvature
      )
    }
  )
p_cod_b2b_round_win_prop
save_plot_for_slide(p_cod_b2b_round_win_prop)
# ## now accounting for number of cod_rounds that end up being played AND series winners...
# cod_rounds |> 
#   filter(win_series, n_rounds > 6L) |> 
#   summarize_b2b_round_wins(n_rounds)
# 
# ## and the losers...
# cod_rounds |> 
#   filter(!win_series) |> 
#   summarize_b2b_round_wins(n_rounds)
```

![](plots/cod_b2b_round_win_prop.png){fig-align="center"}

@@

## Winning a next game given the series state

```{r}
